### 2014-06-25 tex/intro.tex

\newcommand{\Indstate}[1][1]{\State\hspace{#1\algorithmicindent}}

>>>>

In recent years symbolic execution --
a program analysis technique for systematic exploration of
program execution paths using symbolic input values -- has provided
the basis for various software testing and analysis techniques.
For each execution path explored during symbolic execution, constraints
on the symbolic inputs are collected to create a \emph{path
condition}. The set of path conditions computed by symbolic execution
characterize the observed program execution behaviours and can
be used as an enabling technology for various applications, e.g., 
regression 
analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12}, 
data structure repair~\cite{KhurshidETAL05RepairingStructurally}, dynamic
discovery of invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, 
and debugging\cite{Ma:2011}.

Initial work on symbolic execution largely focused on checking 
properties of programs with primitive types, such as integers and 
booleans~\cite{clarke76TSE,King:76}. Despite recent advances
in constraint solving technologies, improvements in
raw computing power, and advances in reduction
and abstraction techniques~\cite{AnandETAL2009AbsSymExe,Godefroid:POPL07}
symbolic execution of programs of modest size containing only
primitive types, remains challenging
because of the large number of execution paths generated
during symbolic analysis.

With the advent of object-oriented
languages that manipulate dynamically allocated data,
 .g., Java and C$++$, recent work has generalized the core ideas of 
symbolic execution to enable analysis of programs containing
complex data structures with unbounded domains, i.e., data stored
on the heap~\cite{Kiasan06,Kiasan07,GSE03}.
These techniques onstruct the heap in a lazy manner, 
deferring materialization of objects on the concrete heap until
they are needed for the analysis to proceed.
%, i.e., until execution of a statement with a  dereference expression 
%($x = r.f$).
Treatment of
heap allocated data then follows concrete program semantics 
once a heap location is materialized, resulting in a large number
of feasible concrete heap configurations, and as a result, a large
number of points of 
non-determinism to be analyzed, further exacerbating 
the state space explosion problem.

THIS PARA IS NOT QUITE RIGHT BUT THE IDEA IS STARTING TO COME OUT.
Although lazy symbolic execution techniques have been instrumental 
in enabling analysis of heap manipulating programs, they miss an
important opportunity to control the state space explosion problem
by treating only inputs with primitive types symbolically and
materializing a concrete heap. As we show in this work, the use of
a fully \emph{symbolic heap} during lazy symbolic execution, 
can improve the scalability of the analysis while maintaining
precision and efficiency. Moreover, the number of path conditions
computed by lazy symbolic execution when a symbolic heap
is used
produces considerably fewer path conditions -- a valuable benefit
for client analyses that use the results of symbolic execution,
e.g., regression analyses.

The key advantages of our approach to lazy symbolic execution
using a fully symbolic heap include:
\begin{itemize}
\item{\emph{Scalability.} Our approach constructs the symbolic
heap on-the-fly during symbolic execution and avoids creating
the additional points of non-determinism
introduced by existing lazy initialization techniques. Moreover, it explores
each execution path only once for any given set of isomorphic heaps.}
\item{\emph{Precision.} At any given point during symbolic execution, 
the symbolic heap represents the exact set of feasible
concrete heap structures for the program under analysis}
\item{\emph{Expressiveness.} The symbolic heap can represent recursive 
data structures  and heap structures resulting from loops and recursive control 
structures in the analyzed code. }
 \end{itemize}

This paper makes the following contributions:

\begin{itemize}
\item{We present a novel lazy symbolic execution technique
 for analyzing heap manipulating
programs that constructs a fully symbolic representatino of
the heap on-the-fly durig symbolic execution.}
\item{We prove the soundness and completeness of our algorithm...}
\item{We implement our approach in the Symbolic PathFinder tool}
\item{We demonstrate experimentally that our technique improves
the scalability of symbolic execution of heap maninpulating software
over state-of-the-art techniques, while maintaining efficiency and precision.}
  \item{We discuss the benefits of using a symbolic heap that
  can be realized by the client analysis that uses the results of symbolic execution.}
 \end{itemize}

\begin{comment}
\newcommand{\Indstate}[1][1]{\State\hspace{#1\algorithmicindent}}
